
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 
```{r}
library(tidyverse)
df <- read_csv('https://covid19.who.int/WHO-COVID-19-global-data.csv')
df %>% filter(Date_reported == '2021-10-22')
```
```{r}
library(lubridate)
library(gganimate)
d1 <- df %>% group_by(Date_reported, Country) %>% summarise(mean = mean(Cumulative_deaths, na.rm=TRUE))
d2 <- d1 %>% group_by(Date_reported) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3 <- d2 %>% filter(rank <= 3)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country))+
  geom_col()+
  geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
  coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
  labs(title = 'Date_reported {closest_state}', x='', y='Cumulative_deaths', fill='Country')+
  theme(plot.title = element_text(hjust = 1, size = 22),
        axis.ticks.y = element_blank(),
        axis.text.y  = element_blank(), legend.position = "none")+
  transition_states(Date_reported)+
  ease_aes("cubic-in-out")
animate(a1, nframes=400)
```

Hint: 

-  Use `filter` to select the most current date 

-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths


2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
df %>% 
    filter(Country_code %in% c('US','IN','BR')) %>% 
    ggplot(aes(y=Cumulative_deaths,
               x=Date_reported,
               color=Country_code))+ 
    geom_line()+
    geom_point(size=3)+
    geom_text(aes(label = Cumulative_deaths), 
              hjust = -.1, size=5) +
    transition_reveal(Date_reported)
```

3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases? 


4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 


5. Use `transition_reveal` to create three animated graph with the vaccination data at 


https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv


