
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 10: Predictive Modeling - Part 1"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment10.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
```

- Set seed to be 2020. 
- The target variable is `diabetes`
- Partition the data into 80% training and 20% testing.  

-------

2. Practice Decision Tree.  Do the follows:

  - Use `rpart` package, create a decision tree with maximum depth of 3. 
  
  - Calculate the accuracy of the model on the testing data. 
  
  - Plot the tree
  
  - Plot the variable importance by the tree

-------

3. Practice Random Forest.  Do the follows: 

  - Use `randomForest` package, create a random forest of 1000 trees. 
  
  - Calculate the accuracy of the model on the testing data. 
  
  - Plot the variable importance by the forest

-------

4. Compare the testing accuracy of a forest of 1000 trees and a forest of 2000 trees. 

-------

5. Using Caret, create a tree with maximum depth of 3 and forest of 1000 trees. Compare the accuracy of these two models.

-------

6. Plot variable importance by the two models in 5. 

-------

7. (Optional - For extra credits only) Use your own selected data.  Do the follows. 

- Handle missing values if any

- Put the variables in the right format (categorical vs. continuous)

- Select a binary target variable (Use can create a binary target variable from a continuous variable). 

- Using caret with method `ranger` to train then test the accuracy of a random forest of 1000 trees. 